Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
more edits
edits

Definitions for concretization are shown in Figure~\ref{fig:syntax}. Concretization for a \sysname policy takes as input, the policy and a context
$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that ``owns" the prefix.
%
For each regular expression $r$, the abstract location is replaced with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%

@@

The goal of the proof is to show that the concretization and compilation functions commute. One can concretize an abstract policy and then compile the concrete result, or compile an abstract policy and the concretize the abstract result and know that the results are the same. In particular, we are interested in establishing the following theorem:

@@

\para{Product Graphs (Step 1)} First, we establish several facts about the relationship of the concrete and abstract product graphs given the definition for building the product graph. We start by assuming that both an abstract constraint and its concretized form are compiled to product graphs and preference functions: 
%
\[
\begin{array}{lll}
  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
\end{array}
\]
%
$L$ can be thought of as a set of locations that ``own" the prefix. Using these assumptions, we show that several relationships hold between $PG$ and $PG^A$ as well as between $\Pref$ and $\Pref^A$. In particular, we show that there is a homomorphism $f_{pg}$ from $PG$ to $PG^A$, and then using this fact, we demonstrate that the inferred local preference functions $\Pref$ and $\Pref^A$ have the property that for all nodes $m$,  $\Pref(m) = \Pref^A(f_{pg}(m))$.

@@

\para{Substitution of Policies (Step 3)} Finally, this theorem is lifted to \sysname policies $pol = p_1, \ldots, p_n$ using the proof from part 2 for individual constraints to obtain the final theorem:
%
$$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$ 
%
The proof is obtained from a simple unfolding of the definition of compilation and concretization.

@@

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by homomorphism} & & \\
  \end{array} \]

\emph{Case $r_1 \cup r_2$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r_1 \cup r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f) \cup con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \cup \Lang(con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \vee p \in \Lang(con(r_1,\Gamma,f)) 
       &\iff& 
       f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
    \text{by cases + IH} & & \\
  \end{array} \]

@@

\emph{Case $!r$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(!r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Lang(!con(r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Sigma^* - \Lang(con(r,\Gamma,f)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
    \text{by IH} & & \\
  \end{array} \]

@@

\begin{defn}
Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:

@@

@@

    \noindent
    Clearly this follows by the definition of list $\mathrm{append}$ and the given equality from Theorem 11.

>>>>

Definitions for concretization are shown in Figure~\ref{fig:syntax}. Concretization for a \sysname policy takes as input, the policy and a context
$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that ``owns" the prefix.
%
For each regular expression $r$, the abstract location is replaced with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}(l) = \{ l' ~\vert~ f(l') = l \}$. For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%

@@

The goal of the proof is to show that the concretization and compilation functions commute. One can concretize an abstract policy and then compile the concrete result, or compile an abstract policy and the concretize the abstract result and know that the configurations will be the same. More specifically, we are interested in establishing the following theorem:

@@

\para{Product Graphs (Step 1)} First, we establish several facts about the relationship of the concrete and abstract product graphs given the definition for building the product graph. We start by assuming that both an abstract constraint and its concretized form are compiled to product graphs and preference functions: 
%
\[
\begin{array}{lll}
  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
\end{array}
\]
%
where $L$ can be thought of as a set of destination locations (possibly $\Sigma$) for the prefix. Using these assumptions, we show that several relationships hold between $PG$ and $PG^A$ as well as between the inferred preference functions $\Pref$ and $\Pref^A$. In particular, we show that there is a homomorphism $f_{pg}$ from $PG$ to $PG^A$, and then using this fact, we demonstrate that the inferred local preference functions $\Pref$ and $\Pref^A$ have the property that for all nodes $m$ in $PG$,  $\Pref(m) = \Pref^A(f_{pg}(m))$.

@@

\para{Substitution of Policies (Step 3)} Finally, this theorem is lifted to \sysname policies $pol = p_1, \ldots, p_n$ using the proof from part 2 for individual constraints to obtain the final theorem:
%
$$\Con(\Compile(pol,G^A),\Gamma,f,G) = \Compile(\Con(pol,\Gamma,f), G)$$ 
%
The proof is obtained by unfolding of the definition of compilation and concretization and applying the previous theorem.

@@

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by the homomorphism} & & \\
  \end{array} \]

\emph{Case $r_1 \cup r_2$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r_1 \cup r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f) \cup con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \cup \Lang(con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \vee p \in \Lang(con(r_1,\Gamma,f)) 
       &\iff& 
       f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
    \text{by cases and the IH} & & \\
  \end{array} \]

@@

\emph{Case $!r$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(!r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Lang(!con(r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Sigma^* - \Lang(con(r,\Gamma,f)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
    \text{by the IH} & & \\
  \end{array} \]

@@

\begin{defn}
Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:

@@

    \noindent
    From the definition of list $\mathrm{append}$ and the given equality from Theorem 11 shown above, we obtain the right hand side.

@@
